### 2015-07-09 src/misc/s6_thanks.tex
Added Lisbon people to the list.

First of all, I would like to extend my thanks to \textbf{my supervisors}, Pieter and Luc, who have been of crucial importance in designing, running, and writing up the experiments in this thesis as well as to my development as a researcher in general. Thanks to \textbf{my fiancee} Daphne and \textbf{my parents}, Marja en Wim, for their unconditional support and confidence in me while I was writing this thesis.

@@

During my PhD I've started to explore the world, my trips wouldn't have been as enjoyable without 
\textbf{ECVP; Alghero and Bremen} Anouk, Bronagh, Chayada, Richard, Simon-Jan, and Xuyan,
\textbf{K\"oln} Verena, Mathias, Sybrine, Marlene, and Lisa,
\textbf{Les Sybelles} Anke Marit, Lisa, Rene, Roemer, Ruud, Sasha, Sybrine, Tim, and Tjerk.
\textbf{London} Ricarda,
\textbf{Oxford} De Stagekamer; Emily, Frauke, Heleen, Katharina, Lisa, Miriam, Roemer, Susanne, and Vincent
\textbf{S\~ao Paulo} Vit\'oria and Kris,
\textbf{T\"ubbingen} Sybrine.
I would like to thank Frank and Verena in particular for the awesome trip to the \textbf{United States} that started it all.

% Johanna, Alessandra

>>>>

First of all, I would like to extend my thanks to \textbf{my supervisors}, Pieter and Luc, who have been of crucial importance in designing, running, and writing up the experiments in this thesis as well as to my development as a researcher in general. Thanks to \textbf{my Daphne} and \textbf{my parents}, Marja en Wim, for their unconditional support and confidence in me while I was writing this thesis.

@@

During my PhD I've started to explore the world, my trips wouldn't have been as enjoyable without
\textbf{ECVP; Alghero and Bremen} Anouk, Bronagh, Chayada, Richard, Simon-Jan, and Xuyan,
\textbf{K\"oln} Verena, Mathias, Sybrine, Marlene, and Lisa,
\textbf{Les Sybelles} Anke Marit, Lisa, Rene, Roemer, Ruud, Sasha, Sybrine, Tim, and Tjerk.
\textbf{London} Ricarda,
\textbf{Oxford} De Stagekamer; Emily, Frauke, Heleen, Katharina, Lisa, Miriam, Roemer, Susanne, and Vincent
\textbf{S\~ao Paulo} Vit\'oria and Kris,
\textbf{T\"ubbingen} Sybrine.
I would like to thank Frank and Verena in particular for the awesome trip to the \textbf{United States} that started it all.
Finally, thanks to Christian, Sylvia, Rida, Mark, Ross, and Pedro, whom I met during my frequent trips to \textbf{Lisboa} in the final stages of my PhD.
